Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-01-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
SoA edited
Deleted section of desirable features described in the other paper.

The web used as a resource for distributed computing has a
long history, and almost since the beginning it was used for
evolutionary computation even before JavaScript was
introduced as a browser-based scripting language in 1997. Before that
time other technologies,
 including Flash animations and VBScript, ActiveX or Java applets were
used; for instance, Java was pointed out in \cite{soares1998get} as a
``language for the internet'', providing some advantages such as multi-architecture compatibility or
security mechanisms, and was proposed in \cite{chandy1996world} as the
basis for the creation of a world-wide peer to peer system using compiled Java
programs. The ATLAS system
\cite{Baldeschwieler:1996:TIG:504450.504482} also used Java together
with another language called Cilk; all these papers indicated that
the introduction of an architecture-independent system such as the
Java virtual machine opened the doors for ultrascale, Internet-wide,
metacomputers. 
%% We need to only reference this section?:
%%------------------- BEGIN
This paper % (Paloma) No really need for that "also", plus it complicates reading
establishes the desirable features of
any {\em global computing} infrastructure, that can also be applied to
distributed evolutionary computation experiments that rely on
volunteer computing: scalability, heterogeneity, fault tolerance,
adaptive parallelism, volunteer's safety, anonymity, hierarchy, ease of use, and
reasonable performance. But hierarchy, this is, the capability of
preferentially using resources in the same organization, is a feature
that could be either disregarded or included within adaptivity, which
leaves us with eight desirable properties. 
% (Paloma) Re-write. For example, "But is hierarchy, this is, the
% capability of preferentially using resources in the same
% organization, the one that could be either disregarded or included
% in adaptivity, which leaves us with eight desirable properties." 
% (Paloma) And I re-wrote what I proposed yesterday.
% thanks :-) -JJ
%%------------------- END
%% EDIT:
%%------------------- BEGIN
The fulfillment of these properties could be achieved by using any of the
languages and associated technologies mentioned above, provided that the user had
installed the required virtual machine plugin first. 
%%------------------- END
% (Paloma) These should be separate sentences
However, embedding a
distributed computation client in the browser has the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed by using desktop applications. 
Baratloo et al. tried in 1996 to create a framework with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1999charlotte}. This framework, which implemented a
distributed shared memory, was inspired by a previous work
on parallel computing libraries PVM and MPI and solved most of the issues by
using the Java virtual machine embedded in the browser,
which provided
security to the user, uniformity of computing environment
independently of the operating system, and access to a common data store in the
server. Additionally, since the Java virtual machine is a sandbox, it was safe to the user
and as it runs compiled bytecode it also guaranteed a certain level of
performance. % (Paloma) I've changed a bit this sentence to unify the use of past tense when talking about Charlotte
Other issues such as scheduling, which are related to adaptive 
parallelism, were solved on the server. It is interesting to note that,
even in the early stages of the web, the possibility of
% (Paloma) Re-write. For example, "but it is interesting to note that, even in the early stages of the web, the possibility of..."
browser-based distributed computing was already researched.

>>>>

The web used as a resource for distributed computing has a
long history, and almost since the beginning it was used for
evolutionary computation even before JavaScript was
introduced as a browser-based scripting language in 1997. Before that
time other technologies,
 including Flash animations and VBScript, ActiveX or Java applets were
used; for instance, Java was pointed out in \cite{soares1998get} as a
``language for the internet'', providing some advantages such as multi-architecture compatibility or
security mechanisms, and was proposed in \cite{chandy1996world} as the
basis for the creation of a world-wide peer to peer system using compiled Java
programs. The ATLAS system
\cite{Baldeschwieler:1996:TIG:504450.504482} also used Java together
with another language called Cilk; all these papers indicated that
the introduction of an architecture-independent system such as the
Java virtual machine opened the doors for ultrascale, Internet-wide,
metacomputers. 
%% We need to only reference this section?:
%%------------------- BEGIN
% This paper % (Paloma) No really need for that "also", plus it complicates reading
% establishes the desirable features of
% any {\em global computing} infrastructure, that can also be applied to
% distributed evolutionary computation experiments that rely on
% volunteer computing: scalability, heterogeneity, fault tolerance,
% adaptive parallelism, volunteer's safety, anonymity, hierarchy, ease of use, and
% reasonable performance. But hierarchy, this is, the capability of
% preferentially using resources in the same organization, is a feature
% that could be either disregarded or included within adaptivity, which
% leaves us with eight desirable properties. 
% % (Paloma) Re-write. For example, "But is hierarchy, this is, the
% % capability of preferentially using resources in the same
% % organization, the one that could be either disregarded or included
% % in adaptivity, which leaves us with eight desirable properties." 
% % (Paloma) And I re-wrote what I proposed yesterday.
% % thanks :-) -JJ
% %%------------------- END
% %% EDIT:
% %%------------------- BEGIN
% The fulfillment of these properties could be achieved by using any of the
% languages and associated technologies mentioned above, provided that the user had
% installed the required virtual machine plugin first. 
% %%------------------- END
The fulfillment of the desirable features of any distributed evolutionary 
computation experiments that rely on volunteer computing \cite{2016arXiv160101607M} could be achieved by using any of the
languages and associated technologies, mentioned above, provided that the user had
installed the required virtual machine plugin first.

% (Paloma) These should be separate sentences
However, embedding a
distributed computation client in the browser has the advantage of
providing a single and universal way of accessing resources via an
URI, something that is not guaranteed by using desktop applications. 
Baratloo et al. tried in 1996 to create a framework with
the aforementioned qualities called {\em Charlotte}
\cite{baratloo1999charlotte}. This framework, which implemented a
distributed shared memory, was inspired by a previous work
on parallel computing libraries PVM and MPI and solved most of the issues by
using the Java virtual machine embedded in the browser,
which provided
security to the user, uniformity of computing environment
independently of the operating system, and access to a common data store in the
server. Additionally, since the Java virtual machine is a sandbox, it was safe to the user
and as it runs compiled bytecode it also guaranteed a certain level of
performance. % (Paloma) I've changed a bit this sentence to unify the use of past tense when talking about Charlotte
Other issues such as scheduling, which are related to adaptive 
parallelism, were solved on the server. It is interesting to note that,
even in the early stages of the web, the possibility of
% (Paloma) Re-write. For example, "but it is interesting to note that, even in the early stages of the web, the possibility of..."
browser-based distributed computing was already researched.
